---
output: github_document
---

# qualtables

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = '#>',
  fig.path = 'man/figures/README-',
  out.width = '100%',
  warning = FALSE,
  message = FALSE
)
```

This is under development. If you find bugs or wish to collaborate, please contact me at svenpubmail@gmail.com

*Huge thank you to authors of [qualtRics](https://github.com/ropensci/qualtRics). Appreciate learn/steal-ing your `httr` code*

`qualtables` is a library that can retrieve data about Qualtrics surveys
extracted from the API. You can generate tables that describe the questions,
blocks, choices, and exported columns of a survey. This is particularly useful
for checking that the survey is configured correctly or comparing surveys.

Install it like this:

```{r, eval = FALSE}
devtools::install_github('svenhalvorson/qualtables')
```

These two environment variables (should be accessible by `Sys.getenv`) need to be set in the same way that the [qualtRics](https://github.com/ropensci/qualtRics) library uses them:

1. `QUALTRICS_API_KEY`: 'your_api_key'
2. `QUALTRICS_BASE_URL`: 'oregon.ca1.qualtrics.com' (depends on organization)


### Flatten a survey  
The function `flatten_survey` creates a semi-curated version of the survey definitions from [this API call](https://api.qualtrics.com/9d0928392673d-get-survey). Use a survey ID (can be found in the URL) to flatten the survey into three tables:

```{r}
survey_id = 'SV_bg4hf9VdW9CwmiO'

survey_flat = qualtables::flatten_survey(survey_id)
```

Here are *a few* of the columns in the questions table:

```{r}
survey_flat[['questions']] |> 
  dplyr::select(question_id, question_description, question_type, question_selector) |>
  head()

```

And the choices table:
```{r}
head(survey_flat[['choices']])
```

There is also a blocks table which is typically less interesting (but still useful).

### Simplify question types    
The next function, `simplify_qtypes`, makes a list of all the questions
and assigns some flags to them. It will tell you if a question is a matrix,
side-by-side (sbs), or is part of a loop-and-merge. It categorizes the questions 
by `question_style`. This can accept either the 
`survey_id` or a flattened survey (faster).

```{r}
survey_qtypes = qualtables::simplify_qtypes(survey_flat = survey_flat)
head(survey_qtypes)
```

### Get a column map  
When working with survey responses, I found it useful to know the associations
between what Qualtrics exports and the question attributes. Here we call 
`get_column_map`:

```{r}
column_map = qualtables::get_column_map(survey_id)

column_map |>
  dplyr::select(column_exported, column_harmonized, choice, question_id) |>
  head()
```

The first column of this data frame is the columns of the data
set that qualtrics gives when responses are exported. Some of the variables
are attributes of that column such as the associated `choice`, `subq_number`,
and `column_number`. Other variables, like `column_harmonized` & `question_name`, 
are ones qualtables generates. I tried to make some question names and 
suffixes that could be used if you do not want to define them yourself.
You an use the "dictionary style" renaming and label functions:

```{r}
responses = qualtables::get_responses(survey_id)

responses = qualtables::rename_dict(
  df = responses,
  old_names = column_map[['column_exported']],
  new_names = column_map[['column_harmonized']]
)

responses = qualtables::var_lab_dict(
  df = responses,
  column_names = column_map[['column_harmonized']],
  var_labs = column_map[['variable_label']]
)
```
