---
output: github_document
---

# qualtreats
Process, organize, and document data from Qualtrics

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = '#>',
  fig.path = 'man/figures/README-',
  out.width = '100%',
  warning = FALSE,
  message = FALSE
)

```

Install like this:

```{r, eval = FALSE}

devtools::install_github('svenhalvorson/qualtreats')

```

These two environment variables (should be accessible by `Sys.getenv`) need
to be set in the same way that the [qualtRics library](https://github.com/ropensci/qualtRics) uses them:

1. `QUALTRICS_API_KEY` = 'your_api_key'
2. `QUALTRICS_BASE_URL` = '....qualtrics.com'

The function `flatten_survey` creates a semi-curated version of the survey definitions from [this API call](https://api.qualtrics.com/9d0928392673d-get-survey). Set a survey ID and flatten the survey into three tables:

```{r}

survey_id = 'SV_bg4hf9VdW9CwmiO'

survey_flat = qualtreats::flatten_survey(survey_id)

survey_flat[['questions']] |> 
  dplyr::select(question_id, question_description, question_type, question_selector) |>
  head()

```


```{r}

head(survey_flat[['choices']])

```

The next function, `simplify_qtypes`, makes a list of all the questions
and assigns some flags to them. I characterized the question attributes in the
column `question_style`. This can accept either the `survey_id` or a flattened
survey (faster).

```{r}

survey_qtypes = qualtreats::simplify_qtypes(survey_flat = survey_flat)
head(survey_qtypes)
```

When working with survey responses, I found it useful to know the associations
between what Qualtrics exports and the question attributes. Here we call 
`get_column_map`:

```{r}

column_map = qualtreats::get_column_map(survey_id)

column_map |>
  dplyr::select(column_exported, column_harmonized, choice, question_id) |>
  head()
```

The first column of this data frame is the columns of the data
set that qualtrics gives when responses are exported. Some of the columns
are attributes of that column such as the associated `choice`, `subq_number`,
and `column_number`. Other columns, like `column_harmonized` & `question_name`, 
are ones qualtreats generates. These may help with renaming and labels:

```{r}

responses = qualtreats::get_responses(survey_id)

responses = qualtreats::rename_dict(
  df = responses,
  old_names = column_map[['column_exported']],
  new_names = column_map[['column_harmonized']]
)

responses = qualtreats::var_lab_dict(
  df = responses,
  column_names = column_map[['column_harmonized']],
  var_labs = column_map[['variable_label']]
)

```
